Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-01-02 Ben_Manuscripts/structure_paper/Draft.tex
Added some extra subsection headings based on Rich's feedback. They'll need editing

  \subsection{Determining the Spatial Configuration of Monomers}

@@

@@

@@

  \subsection{Pore Structure Depends on Initial Configuration}

>>>>

  \subsection{Determining the Number of Monomers per Layer}

@@

  \subsection{Determining Definition of Layers}

@@

  \subsection{Determination of Relative Interlayer Head Group Orientation}

@@

  \subsection{Pore Structure Depends on Initial Configuration}  % Addresses pore definition
